---
title: 'Example 1: Standard Error of a Coefficient'

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,tidy.opts=list(width.cutoff=60))

```

## Setting Up

First load the data and R functions you need into the R workspace.



```{r results = "hide", echo=TRUE, message=FALSE}
load("PlayData_for_Examples.RData") ### load the data for the examples
source("LoadFunctions.R") #### Source the functions required to run the block bootstrap



```

#Motivation/ Statement of Research Problem

What effect does temperature have on the "response" (e.g. Ant body weight)? (MADE UP DATA!!). For this example response is a normally distributed continuous variable. 

In statistical terms this means we want to calculate a confidence interval of the coefficient of temperature (So we need to estimate $\beta$ and se($\beta$))

Lets look at the data:
```{r include=FALSE}
library(ggplot2)
library(gstat)
library(sp)
x.range=range(x)
y.range=range(y)
grd <- expand.grid(x = seq(from = x.range[1], to = x.range[2], by = 0.01), y = seq(from = y.range[1], to = y.range[2], by = 0.01))  # expand points to grid
coordinates(grd) <- ~x + y
gridded(grd) <- TRUE
xy=SpatialPoints(coords=cbind(x,y))
idw <- idw(formula = dat$temperature ~ 1, locations = xy, newdata = grd)  # apply idw model for the data
## [inverse distance weighted interpolation]
idw.output = as.data.frame(idw)  # output is defined as a data table
names(idw.output)[1:3] <- c("long", "lat", "var1.pred")  # give names to the modelled variables
```
```{r echo=FALSE, message=FALSE}
ggplot() + geom_tile(data = idw.output, aes(x = long, y = lat, fill = var1.pred))+scale_fill_gradient2(low="blue", high="red", guide = guide_legend(title="temp")) +  geom_point(data = dat, aes(x = x, y = y, colour=response)) 
#ggsave("Exploration_plot_example1.pdf")

```

A presence/ absence response might look like this:

```{r echo=FALSE, message=FALSE}
ggplot() + geom_tile(data = idw.output, aes(x = long, y = lat, fill = var1.pred))+scale_fill_gradient2(low="blue", high="red", guide = guide_legend(title="temp")) +  geom_point(data = dat, aes(x = x, y = y, colour=as.factor(PresAbsresponse)) )
#ggsave("Exploration_plot_example1.pdf")

```

Plot the response against temperature:

```{r echo=TRUE, message=FALSE}
plot(response~temperature, data=dat)

#add the line of best fit
fit1 = lm ("response~temperature", data=dat)
abline(fit1,col="red")
```