---
title: 'Example 3: Community-level Hypothesis Test using BlockBootID with mvabund,
  block length selection'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,tidy.opts=list(width.cutoff=40))

```

## Setting Up


First load the data and R packages you need into the R workspace.



```{r results = "hide", echo=TRUE, message=FALSE}
load("PlayData_for_Examples.RData") ### load the data for the examples
source("LoadFunctions.R") #### Source the functions required to run the block bootstrap


#Install packages if required
if(!require(mvabund)) { install.packages("mvabund", repos =
"http://cran.us.r-project.org"); require(mvabund) }

library(mvabund)


```

#Motivation


```{r pressure, echo=TRUE}
set.seed(42)
treatment =rbinom(500,1,0.5)
multispecies_dat = data.frame(multispecies_dat,treatment)
```

## Coding StatFunction argument
Define MultSpeciesTestStat a function which will be the *StatFunction* argument to *BlockBootApply*. 
```{r funct, echo=TRUE}

MultSpeciesTestStat = function(dat){
responseMultiSpecies = mvabund(dat[,1:20])

null.model = manyglm (responseMultiSpecies~1, data=dat, family="binomial")
alt.model = manyglm (responseMultiSpecies~temperature*treatment, data=dat, family="binomial")
Test.stat = sum(alt.model$two.loglike) - sum(null.model$two.loglike)
;
Test.stat
}

MultSpeciesTestStat (multispecies_dat)

```
## Run Block Bootstrap

Run Block Bootstrap, using Lahiri method of block size selection. We search over 4 blocks sizes (0- i.e. IID, 0.05, 0.1, 0.2). BlockBootApply uses the size which minimises the Empirical MSE of SE(T), where T is the multispecies likelihood ratio test statistic. Use 0.05 as tuning block length, (tuning\_block\_length =2). 

```{r ,  echo=TRUE}

lookuptables.folderpathname = "LookupTables/" 

```
 
```{r ,  echo=TRUE}


Results.Example3 = BlockBootApply (x = x ,y = y ,block_Ls = c(0,0.05,0.1,0.2), Grid_space = 0.01 ,
dat = multispecies_dat , Stat.function = MultSpeciesTestStat,  tuning_block_length = 2, NBoot = 2, 
method.block.length.select = "Lahiri",  type="SE", lookuptables.folderpath=lookuptables.folderpathname)


L.example3  = Results.Example3$Lahiri_block_size
#The chosen block size parameter
L.example3

```

Now make a bootID matrix and feed into mvabund::summary. 


```{r , echo=TRUE}
BootID.example3 = BlockBootID(x = x ,
y = y,
block_Ls = L.example3,
NBoot = 500,
Grid_space = 0.01,
lookuptables.folderpath =  lookuptables.folderpathname, shape="disc")

#######

responseMultiSpecies = mvabund(multispecies_dat[,1:20])

mod.full  = manyglm(responseMultiSpecies~temperature*treatment, data = multispecies_dat,
family="binomial")

anova(mod.full, bootID = BootID.example3, resamp="case")

##########
