---
title: 'Example 2: Community-level Hypothesis Test using BlockBootID with mvabund'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Setting Up

First load the data and R packages you need into the R workspace.



```{r results = "hide", echo=TRUE, message=FALSE}
load("PlayData_for_Examples.RData") ### load the data for the examples
source("LoadFunctions.R") #### Source the functions required to run the block bootstrap


#Install packages if required
if(!require(mvabund)) { install.packages("mvabund", repos = "http://cran.us.r-project.org"); 
require(mvabund) }
library(mvabund)


```

#Motivation

We want to test an assemblage/ community of species for the significance of a bunch of variables, using ``mvabund::summary''.


This example assumes a block size is selected by the user already, from either pilot study or as in Example 3. They can then use \textbf{BlockBootID} to generate an ID matrix for input into mvabund.



```{r pressure, echo=TRUE}
set.seed(42)

lookuptables.folderpathname = "LookupTables/" 

######## Get a bootID matrix (takes a minute or two)
BootID.example2 = BlockBootID(x = x ,
                              y = y,
                              block_Ls = 0.1,
                              NBoot = 500,
                              Grid_space = 0.01,
                              lookuptables.folderpath =  lookuptables.folderpathname)
```
## Run hypothesis test/ summary in mvabund


##running time <2 minutes


```{r variogram, echo=TRUE}
responseMultiSpecies=mvabund(multispecies_dat[,1:20]) #20 species multivariate reponse
mod.1  = manyglm(responseMultiSpecies~temperature, data = multispecies_dat,family="binomial")
mod.2  = manyglm(responseMultiSpecies~temperature*treatment, data = multispecies_dat,family="binomial")
anova.results = anova(mod.1, mod.2, bootID=BootID.example2, resamp="case")
anova.results

```
The treatment is not significant. 

