---
title: 'Example 1: Standard Error of a Coefficient'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,tidy.opts=list(width.cutoff=60))

```

## Setting Up

First load the data and R functions you need into the R workspace.



```{r results = "hide", echo=TRUE, message=FALSE}
load("PlayData_for_Examples.RData") ### load the data for the examples
source("LoadFunctions.R") #### Source the functions required to run the block bootstrap



```

#Motivation

Imagine we want to know the standard error of our estimate for $\beta$- the coefficient of temperature. First fit the model.  

```{r pressure, echo=TRUE}
set.seed(42)


fit1 = lm (response ~ temperature, data = dat)
summary(fit1)
```
## Getting Variogram Practical Range
Fit a variogram on the residuals- notice we can see spatial autocorrelation. 
Use the variogram practical range as a tuning parameter for the Lahiri method of block selection. 
Always check the variogram visually. Sometimes you may need to change max.dist, breaks or initial conditions to get a sensible practical range. It is hard to automate this process.
```{r variogram, echo=TRUE}

ini.vals <- expand.grid(seq(0,10,l=100), seq(0,1,l=100)) #inital values for variofit
variogram_block_length = select_b_length_off_variogram_envelope(x,y,resids = fit1$resid, 
max.dist = 0.4, breaks=c(0,0.025,0.05,0.075,0.1,0.15,0.2,0.3,0.4,0.5,0.6,0.7,0.8,1.5),ini=ini.vals)


variogram_block_length

```
## Coding StatFunction argument
Define BetaCoeff a function which will be the *StatFunction* argument to *BlockBootApply*. BetaCoeff 
gets a coefficient for temperature for inference
```{r funct, echo=TRUE}



BetaCoeff = function(dat){
  fit1 = lm ("response~temperature", data=dat)
  Beta = fit1$coefficients["temperature"]
  Beta
}

```
## Run Block Bootstrap

First the user should create a folder called e.g. LookupTables in their R working directory. As all the examples below use the same site coordinates they all share the same lookup tables. However if a new analysis is being done on different data (with different site co-ordinates), then a new lookup table needs to be created. 

```{r ,  echo=TRUE}

lookuptables.folderpathname = "LookupTables/" 

```
Run Block Bootstrap, using Lahiri method of block size selection, with the variogram to select the tuning parameter. We search over 4 blocks sizes (0- i.e. IID, 0.05, 0.1, 0.2). BlockBootApply uses the size which minimises the Empirical MSE of SE($\beta$). Use 0.2 as tuning block length as per variogram practical range (tuning block length =4). 
```{r ,  echo=TRUE, warning=FALSE, message=FALSE}
Results = BlockBootApply (x = x ,y = y ,block_Ls = c(0,0.05,0.1, 0.2), Grid_space = 0.01 , 
                          dat = dat ,
                          Stat.function = BetaCoeff,  tuning_block_length = 0.2, 
                          NBoot = 500, method.block.length.select = "EmpiricalMSE",
                          type="SE", lookuptables.folderpath=lookuptables.folderpathname)


```


Check sensitivity to tuning parameter. See that some columns are minimised by block length 0.1, and some columns by 0.05 so tuning block length was imporant here
```{r , echo=TRUE}

Results$Empirical.MSE
```
The block size parameter chosen is:

```{r, echo=TRUE}
Results$EmpiricalMSE_block_size
```
This is the standard error (estimated via block bootstrap to account for spatial autocorrelation) of $\beta$

```{r , echo=TRUE}
Results$SE.estimate.EmpiricalMSE_block_size
```

